A Logistic Regression Prediction of 2024 Election Odds Gives VP Harris a 38.3% Winrate

### 2024-11-04 paper/paper.qmd
updated paper and references

We use the statistical programming language R [@R] for the graphing, analysis and presentation of the project as a whole. Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], lubridate [@lubridate] and pROC [@pROC] were used directly in the analysis of the data. Tidyverse [@tidyverse], stringr [@stringr], dplyr [@dplyr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.

@@

```
The regression coefficients for the logistic and linear models are presented in the Appendix because they are not the outcome of interest.

>>>>

We use the statistical programming language R [@R] for the graphing, analysis and presentation of the project as a whole. Caret [@caret], glmnet [@glmnet; @glmnet2; @glmnet3], nnet [@nnet], lubridate [@lubridate] and pROC [@pROC] were used directly in the analysis of the data. Tidyverse [@tidyverse], stringr [@stringr], dplyr [@dplyr], gt [@gt], knitr [@knitr], and styler [@styler] were used in the presentation and/or styling of the data, graphs, and paper as a whole.

@@

The regression coefficients for the logistic and linear models are presented in the Additional Data Details section (@sec-model-details) because they are not the outcome of interest.
